---
title: "Dashboard for thyroid"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: lumen
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(skimr)
library(readr)

library(ggplot2)
library(plotly)
```

```{r}
# 1.Importation des données
data1 <- read.csv("A_Datas/thyroid_tidy.csv",encoding = 'UTF-8')
data2 <- read.csv("A_Datas/df_tidy_for_db3.csv")
data2_1 <- read.csv("A_Datas/df_tidy_for_db2_1.csv") # for db2
data2_2 <- read.csv("A_Datas/df_tidy_for_db2_2.csv") # for db2
data3 <- read.csv("A_Datas/df_tidy_for_db2.csv")
thyroid <- read_csv("A_Datas/thyroid_tidy.csv")
raw <- read_csv("A_Datas/thyroid.csv")
raw <- rename(raw, c("T3_reading_fill" = "T3_reading", "T4_reading_fill" = "T4_reading", "TSH_reading_fill" = "TSH_reading", "FTI_reading_fill" = "FTI_reading",  "T4U_rate_reading_fill" = "thyrox_util_rate_T4U_reading"))
```




Ⅰ.Recap
=======================================================================


Column {.sidebar}
-----------------------------------------------------------

Please enter the patient's number

```{r}
numericInput(inputId = 'Patient_number', label = "Patient's number", value = 1, min = 1, max = nrow(thyroid), step = 1)
```


Row
-----------------------------------------------------------


### Patient's gender

```{r}
renderValueBox({
  valueBox(
    value = if (thyroid[input$Patient_number,]$patient_gender == 1) "Woman" else "Man",
    caption = "Gender", 
    icon = "fa-venus-mars",
    color = if (thyroid[input$Patient_number,]$patient_gender == 0) "MediumTurquoise" else "PeachPuff"
)})

renderValueBox({
    valueBox(
      value = if (thyroid[input$Patient_number, ]$pregnant == 1) { "Pregnant" },
      color = if (thyroid[input$Patient_number,]$patient_gender == 0) "MediumTurquoise" else "PeachPuff"
    )
  })

```

### Patient's age {.value-box}


```{r}
renderValueBox({
  valueBox(
    value = thyroid[input$Patient_number,]$patient_age,
    caption = "Age",
    icon = "fa-user",
    color = if (thyroid[input$Patient_number,]$patient_gender == 0) "MediumTurquoise" else "PeachPuff"
)})
```

### Thyroïd state {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = if (thyroid[input$Patient_number,]$ThyroidClass == "negative") "Healthy" else "Sick",
    icon = "fa-notes-medical",
    color = if (thyroid[input$Patient_number, ]$ThyroidClass == "sick") "DarkRed" else if (thyroid[input$Patient_number,]$patient_gender == 0) "MediumTurquoise" else "PeachPuff"
)})
```


### Patient's referral source

```{r}
renderValueBox({
    valueBox(
      value = thyroid[input$Patient_number, ]$ref_src,
      icon = 'fa-asterisk',
      color = if (thyroid[input$Patient_number,]$patient_gender == 0) "MediumTurquoise" else "PeachPuff"
    )
  })
```




Row
-----------------------------------------------------------



### T4 rate
```{r}
renderGauge({
  gauge(
    value = thyroid[input$Patient_number,]$T4_reading_fill,
    min = 0,
    max = max(thyroid$T4_reading_fill),
    sectors = gaugeSectors(success = c(80, 140), 
                         warning = c(0, 80), 
                         danger = c(140, max(thyroid$T4_reading_fill)),
                         colors = c("PaleGreen", "Crimson", "Crimson")),
    symbol = 'U',
    label = if (thyroid[input$Patient_number, ]$T4_measured == 1) "Real Value" else "Imputed value"
)})
```

### T3 rate
```{r}
renderGauge({
  gauge(
    value = thyroid[input$Patient_number,]$T3_reading_fill,
    min = 0,
    max = max(thyroid$T3_reading_fill),
    sectors = gaugeSectors(success = c(0.6, 2.2), 
                         warning = c(0, 0.6), 
                         danger = c(2.2, max(thyroid$T3_reading_fill)),
                         colors = c("PaleGreen", "Crimson", "Crimson")),
    symbol = 'U',
    label = if (thyroid[input$Patient_number, ]$T3_measured == 1) "Real Value" else "Imputed value"
)})
```

### TSH rate

 
```{r}
renderGauge({
  gauge(
    value = thyroid[input$Patient_number,]$TSH_reading_fill,
    min = 0,
    max = max(thyroid$TSH_reading_fill),
    sectors = gaugeSectors(success = c(0.4, 4), 
                         warning = c(0, 0.4), 
                         danger = c(4, max(thyroid$TSH_reading_fill)),
                         colors = c("PaleGreen", "Crimson", "Crimson")),
    symbol = 'U',
    label = if (thyroid[input$Patient_number, ]$TSH_measured == 1) "Real Value" else "Imputed value"
)})
```


### FTI rate

```{r}
renderGauge({
  gauge(
    value = thyroid[input$Patient_number,]$FTI_reading_fill,
    min = 0,
    max = max(thyroid$FTI_reading_fill),
    sectors = gaugeSectors(success = c(60, 120), 
                         warning = c(0, 60), 
                         danger = c(120, max(thyroid$FTI_reading_fill)),
                         colors = c("PaleGreen", "Crimson", "Crimson")),
    symbol = 'U',
    label = if (thyroid[input$Patient_number, ]$FTI_measured == 1) "Real Value" else "Imputed value"
)})
```

### T4U rate

```{r}
renderGauge({
  gauge(
    value = thyroid[input$Patient_number,]$T4U_rate_reading_fill,
    min = 0,
    max = max(thyroid$T4U_rate_reading_fill),
    sectors = gaugeSectors(success = c(0.7, 0.9), 
                         warning = c(0, 0.7), 
                         danger = c(0.9, max(thyroid$T4U_rate_reading_fill)),
                         colors = c("PaleGreen", "Crimson", "Crimson")),
    symbol = 'U',
    label = if (thyroid[input$Patient_number, ]$thyrox_util_rate_T4U_measured == 1) "Real Value" else "Imputed value"
)})
```


Row 
-----------------------------------------------------------

### Treatments & Operations


```{r}
DT::renderDataTable({
  treat_vect <- c()
  if (thyroid[input$Patient_number, ]$presc_thyroxine == 1) {
    treat_vect <- append(treat_vect, "Thyroxine presciption")
  }
  if (thyroid[input$Patient_number, ]$presc_anthyroid_meds == 1) { 
    treat_vect <- append(treat_vect, "Anti-thyroid medicine presciption")
  }
  if (thyroid[input$Patient_number, ]$radioactive_iodine_therapyI131 == 1) { 
    treat_vect <- append(treat_vect, "Radioactive iodine treatment")
  }
  if (thyroid[input$Patient_number, ]$lithium == 1) { 
    treat_vect <- append(treat_vect, "Lithium treatment")
  }
  if (thyroid[input$Patient_number, ]$thyroid_surgery == 1) {
    treat_vect <- append(treat_vect, "Thyroid surgery")
  }
  if (length(treat_vect) == 0) {
    treat_vect <- append(treat_vect, "No treatments or operations")
  }
  data <- data.frame("Treatments" = treat_vect)
  DT::datatable(data, options = list(
    bPaginate = FALSE
  ))
})
```






### Queries


```{r}
DT::renderDataTable({
  query_vect <- c()
  if (thyroid[input$Patient_number, ]$queried_why_on_thyroxine == 1) {
    query_vect <- append(query_vect, "Query on why is the patient on thyroxine prescription")
  }
  if (thyroid[input$Patient_number, ]$query_hypothyroid == 1) { 
    query_vect <- append(query_vect, "Under active thyroid query")
  }
  if (thyroid[input$Patient_number, ]$query_hyperthyroid == 1) { 
    query_vect <- append(query_vect, "Over active thyroid query")
  }
  if (length(query_vect) == 0) {
    query_vect <- append(query_vect, "No ongoing queries")
  }
  data <- data.frame("Queries" = query_vect)
  DT::datatable(data, options = list(
    bPaginate = FALSE
  ))
})
```




### Symptoms & Diagnosis


```{r}
DT::renderDataTable({
  diag_vect <- c()
  if (thyroid[input$Patient_number, ]$goitre == 1) {
    diag_vect <- append(diag_vect, "Goitre")
  }
  if (thyroid[input$Patient_number, ]$tumor == 1) { 
    diag_vect <- append(diag_vect, "Tumor")
  }
  if (thyroid[input$Patient_number, ]$hypopituitarism == 1) { 
    diag_vect <- append(diag_vect, "Under active thyroid")
  }
  if (thyroid[input$Patient_number, ]$sick == 1) {
    diag_vect <-append(diag_vect, "Sickness due to thyroxine depletion or over activity")
  }
  if (thyroid[input$Patient_number, ]$psych_condition == 1) {
    diag_vect <-append(diag_vect, "Psychological condition")
  }
  if (length(diag_vect) == 0) {
    diag_vect <- append(diag_vect, "No symptoms or diagnosis")
  }
  data <- data.frame("Symptômes et diagnostics" = diag_vect)
  DT::datatable(data, options = list(
    bPaginate = FALSE
  ))
})
```










Ⅱ.Summaries {data-orientation=Columns}
=======================================================================

Column {.sidebar}
------------------------------------------------------------------------

```{r}
selectInput('var', 'Influencing Factors',
            list("Thyroxine replacement prescription" = "presc_thyroxine",
                 "Patient gender" = "patient_gender",
                 "Query on why on thyroxine" = "queried_why_on_thyroxine", 
                 "Sickness due to thyroxine depletion or over activity" = "sick",
                 "Anti-thyroid medicine prescription" = "presc_anthyroid_meds",
                 "Thyroid surgery" = "thyroid_surgery",
                 "Pregnant or not"  = "pregnant",
                 "Radioactive iodine treatment" = "radioactive_iodine_therapyI131", 
                 "Under active thyroid query" = "query_hypothyroid", 
                 "Over active thyroid query" = "query_hyperthyroid", 
                 "Lithium carbonate treatment" = "lithium", 
                 "Goitre" = "goitre", 
                 "Tumor" = "tumor", 
                 "Diagnosed under active thyroid" = "hypopituitarism", 
                 "Psychological condition" = "psych_condition", 
                 "TSH measured" = "TSH_measured", 
                 "T4 measured" = "T4_measured",
                 "T3 measured" = "T3_measured", 
                 "Thyroxine utilisation rate measured" = "thyrox_util_rate_T4U_measured", 
                 "Free Thyroxine Index measured" = "FTI_measured"))
    
# varSelectInput("variable", "Variable:", data)
```



Column {data-height=600}
-----------------------------------------------------------------------
### Comparison of different factors
```{r}
renderPlot({
df_2 <- data3 %>% 
  filter(indicateur == input$var)

df_2$positive[df_2$positive == 0 ]<-"NO"
df_2$positive[df_2$positive == 1 ]<-"YES"

df_2 %>% 
  ggplot(aes(x = positive, y = count)) +
  geom_col(aes(colour=positive, fill=positive), position = "dodge")+
  facet_grid( ~ ThyroidClass) + labs(
    x = " ",
    # title = "Numerical variable comparison",
    subtitle = " ",
    caption = "Data source: Mr.Aymeric Stamm")
})
```

### Repartition of the treatments
```{r}
plot_ly(data2_2, labels = ~type_of_traitement , values = ~proportion, type = 'pie')
```

Column {data-height=600}
-----------------------------------------------------------------------
### Number of sick people in the different age groups
```{r}
p <- ggplot(data=data2_1, aes(x = Age , y = Number, fill = Genre)) +
        geom_bar(stat="identity")
ggplotly(p)
```
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Summary of patients informations
```{r}
data1$ThyroidClass[data1$ThyroidClass == 'sick']<- 1
data1$ThyroidClass[data1$ThyroidClass == 'negative']<- 0

nb_malade <- sum(data1$ThyroidClass==1)
nb_pas_malade <- sum(data1$ThyroidClass==0)

sumup <- data1 %>%
  filter(ThyroidClass==1) %>%
  summarize(prop_malade = sum(ThyroidClass==1)/3772*100,
            prop_femme = sum(patient_gender)/nb_malade*100,
            moyen_age = sum(patient_age)/nb_malade,
            min_age = min(patient_age),
            max_age = max(patient_age))

names(sumup) <- c('negative proportion(%)', 'women proportion(%)', 'age mean', 'age min', 'age max')

renderTable({
  sumup
})

```
### Distribution of the form of the diseases
```{r}
types <- data1 %>% 
  group_by(ThyroidClass) %>% 
  summarize(n_goitre = sum(goitre), n_tumor = sum(tumor), n_sick = sum(sick), n_hypopituitarism = sum(hypopituitarism)) %>% 
  mutate(population = c(nb_pas_malade,nb_malade)) %>% 
  mutate(prop_goitre = n_goitre/population*100, prop_tumor = n_tumor/population*100, prop_sick = n_sick/population*100, prop_hypopituitarism = n_hypopituitarism/population*100)

types <- cbind(types[1], types[6:10])

renderTable({
  types
})
```






Ⅲ.Comparision {data-orientation=Columns}
=======================================================================


Column {.sidebar}
------------------------------------------------------------------

```{r}
type <- c("patient_gender", "presc_thyroxine", "queried_why_on_thyroxine", 
          #"presc_anthyroid_meds", 
          "sick", 
          #"pregnant", "thyroid_surgery", 
          "radioactive_iodine_therapyI131", "query_hypothyroid", "query_hyperthyroid", "lithium", "goitre", "tumor", "hypopituitarism", "psych_condition", "TSH_measured", "T3_measured", 
          # "T4_measured", 
          "thyrox_util_rate_T4U_measured", "FTI_measured")

selectInput('xcol2', 'X Variable', 
            list(
              "Free triiodothyronine (T3) rate" = "T3_reading_fill",       
              "Free thyroxine (T4)" = "T4_reading_fill",     
              "Thyroid Stimulating Hormone (TSH) rate" = "TSH_reading_fill",     
              "Free Thyroxine Index (FTI)" = "FTI_reading_fill",    
              "Thyroxine utilisation rate (T4U)" = "T4U_rate_reading_fill"))

selectInput('ycol2', 'Y Variable',             
            list(
              "Free thyroxine (T4) rate" = "T4_reading_fill",  
              "Free triiodothyronine (T3) rate" = "T3_reading_fill",       
              "Thyroid Stimulating Hormone (TSH) rate" = "TSH_reading_fill",     
              "Free Thyroxine Index (FTI)" = "FTI_reading_fill",    
              "Thyroxine utilisation rate (T4U)" = "T4U_rate_reading_fill"))

selectInput('var2', 'Influencing Factors',
            list("Thyroxine replacement prescription" = "presc_thyroxine",
                 "Patient gender" = "patient_gender",
                 "Query on why on thyroxine" = "queried_why_on_thyroxine", 
                 "Sickness due to thyroxine depletion or over activity" = "sick",
                 "Anti-thyroid medicine prescription" = "presc_anthyroid_meds",
                 "Thyroid surgery" = "thyroid_surgery",
                 "Pregnant or not"  = "pregnant",
                 "Radioactive iodine treatment" = "radioactive_iodine_therapyI131", 
                 "Under active thyroid query" = "query_hypothyroid", 
                 "Over active thyroid query" = "query_hyperthyroid", 
                 "Lithium carbonate treatment" = "lithium", 
                 "Goitre" = "goitre", 
                 "Tumor" = "tumor", 
                 "Diagnosed under active thyroid" = "hypopituitarism", 
                 "Psychological condition" = "psych_condition", 
                 "TSH measured" = "TSH_measured", 
                 "T4 measured" = "T4_measured",
                 "T3 measured" = "T3_measured", 
                 "Thyroxine utilisation rate measured" = "thyrox_util_rate_T4U_measured", 
                 "Free Thyroxine Index measured" = "FTI_measured"))


checkboxInput('NAval', "Display real/imputed values", value = FALSE)


selectInput("variable",  # 传入变量名称
            "Display Radar Chart for presence (Yes) or absence (No) of selected incluencing factor (if gender selected : Yes = F/No = M)", # 提示文字
            list("Yes" = "1",
                 "No" = "0"))
    
# varSelectInput("variable", "Variable:", data)
```




Column {data-width=400}
-----------------------------------------------------------------------
### Comparison of hormone values
```{r, fig.height=10}
renderPlot({
df_2 <- data1 %>% 
  rename(Factor = input$var2) %>% 
  rename(xval = input$xcol2) %>% 
  rename(yval = input$ycol2) %>% 
  
  mutate(xval = log(xval)) %>% 
  mutate(yval = log(yval))


df_2$Factor[df_2$Factor== 1 ]<-"With"
df_2$Factor[df_2$Factor== 0 ]<-"Without"

df_2 %>% 
  ggplot(aes(x = xval, y = yval)) +
  geom_point(aes(colour= if (input$NAval == TRUE) is.na(raw[input$xcol2] & raw[input$ycol2]) else Factor))+
  facet_grid(Factor ~ ThyroidClass) + labs(
    x = "X Variable",
    y = "Y Variable",
    # title = "Numerical variable comparison",
    color = if (input$NAval == TRUE) "Real or Imputed values" else "Influencing Factor",
    subtitle = " ",
    caption = "Data source: Aymeric Stamm"  )
})

```
### Comparison of indicators in different patient groups
```{r}
renderPlot({
  data2 <- data2 %>% 
    filter(p_n == input$variable, indicateur == input$var2) %>% 
    select(-c(p_n, indicateur))

AddRow=c(NA, 
         nrow(data2)+1, 
         data2[1,(ncol(data2)-1):ncol(data2)])
data2 <- rbind(data2, as.numeric(AddRow))


data2 <- data2 %>% 
  mutate(id = c(1:6))
data2  %>%
  ggplot(aes(x=id)) +
  geom_polygon(aes(y=standard),color = "black", fill= "#ffd200",alpha=0.1)+
  geom_point(aes(y=standard, fill= "#ffd200"),size=5,shape=21,color = 'black',fill= "#ffd200")+
  
  geom_polygon(aes(y=mean),color = "black", fill= "#304156",alpha=0.1)+
  geom_point(aes(y=mean, fill= "#304156"),size=5,shape=21,color = 'black', fill= "#304156")+
  
  geom_polygon(aes(y=median),color = "black", fill= "#f8766d",alpha=0.1)+
  geom_point(aes(y=median, fill= "#f8766d"),size=5,shape=21,color = 'black', fill= "#f8766d")+
  
  coord_polar() +
  scale_x_continuous(breaks =data2$id,labels=data2$name)+
  theme_light()+
  theme(axis.text.x=element_text(size = 15,colour="black"))+
    labs(
     x = " ", y = "Hormone values",
    subtitle =  "Tips: Red: Mediam, Yellow: Standard, Gray: Mean" ,
    caption = "T3: The reading result of the Free triiodothyronine | T4: The reading result of the Free thyroxine, \nTSH: The result of the TSH blood test | FTI:The result of the Free Thyroxine Index. \nT4U: The result of the thyroxine utilisation rate" )
})
```


Column {data-width=500}
-----------------------------------------------------------------------
### Comparison of hormone values (X Variable)
```{r}
renderPlot({
  df_2 <- data1 %>% 
  rename(Factor = input$var2) %>%
  rename(xval = input$xcol2)

df_2$Factor[df_2$Factor == 1 ]<-"With"
df_2$Factor[df_2$Factor == 0 ]<-"Without"


df_2 %>% 
  ggplot(aes(x=ThyroidClass, y=xval)) +
  geom_boxplot(aes(colour=Factor))+ 
  labs(
    x = "Illness",
    y = "X Variable")
})
```

### Comparison of hormone values (Y Variable)
```{r}
renderPlot({
  df_2 <- data1 %>% 
  rename(Factor = input$var2) %>%
  rename(yval = input$ycol2)

df_2$Factor[df_2$Factor== 1 ]<-"With"
df_2$Factor[df_2$Factor== 0 ]<-"Without"


df_2 %>% 
  ggplot(aes(x=ThyroidClass, y=yval)) +
  geom_boxplot(aes(colour=Factor))+ 
  labs(
    x = "Illness",
    y = "Y Variable")
})
```

